\documentclass[a4paper, 12pt]{article}
\usepackage{titling}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{hyperref}
\setlength{\heavyrulewidth}{1.5pt}
\setlength{\abovetopsep}{4pt}
\graphicspath{{.}}

\usepackage[margin=1in]{geometry}

% Must be after geometry
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{AIR Homework 8}
\lhead{M. Nguyen, B. Ha \& E. Ovchinnikova}
\cfoot{\thepage}

\setlength{\droptitle}{-5em}

\title{Artificial Intelligence for Robots \\
				- Homework 8 -}
\author{Minh Nguyen, Bach Ha \& Evgenia Ovchinnikova}
\date{Lecture date: 24 November 2015}

\begin{document}

\maketitle

\section{Theoretical questions}

    \begin{itemize}
        \item \emph{What is a solution for a constraint satisfaction problem?}\\
            A solution for a constraint satisfaction problem (CSP) is a state in
            which all variables are assigned and no constraint is violated.
        \item \emph{What are the components of a constraint satisfaction problem?}\\
            A constraint satisfaction problem consists of the variables, the
            domain of these variables, and a set of constraints on these variables.
        \item \emph{What is a constraint and how is it represented?}\\
            A constraint specifies the conditions variables must conform to be a
            solution. A constraint can concern value of a single variable (unary)
            or values of a group of variables. A constraint can be absolute or
            by preference. A constraint operated on a discrete, finite domain
            can be represented by enumerating all possible values or combination
            of values.
        \item \emph{What is a constraint graph?}\\
            A constraint graph is a map representation of a binary CSP (where a
            constraint applies to at most two variables). In a constraint graph,
            each node represents a variable, and each edge represents a constraint.
        \item \emph{What are discrete variables and how are they divided?}\\
            Discrete variables are variables whose values are from a discrete
            domain. Discrete variables can be of finite where variables can have
            be assigned all possible values of the domain, or infinite domains
            like integers. Infinite domains require a constraint language, and
            can be linear or non-linear.
        \item \emph{What is preference?}\\
            As opposed to an absolute constraint, a constraint by preference does
            not fail a state upon violation, but only state which state is
            preferable. Preferences are usually represented by setting a cost
            for each variable assignment.
        \item \emph{What is a successor function?}\\
            A successor function assigns a value to an unassigned variable and
            check if the assignment violates any constraints.
        \item \emph{What is constraint propagation?}\\
            Constraint propagation checks for constraint satisfaction locally
            after each variable assignment.
        \item \emph{What is arc-consistency?}\\
            An arc from X -> Y represents the dependence of Y on the value of X
            to satisfy the constraints between the two variables. X -> Y is
            consistent iff for all values of X, there's at least one allowed
            value for Y.
        \item \emph{What is Backtracking Search?}\\
            Backtracking search is a search algorithm for CSP's which uses depth
            first search to find a solution, but backtracks away from a subtree
            if a violation of the constraints is caused by the variable assignment
            spawning that subtree. The test for violation is done before the
            successor generation step.
    \end{itemize}

\section{Sudoku puzzle}

\begin{itemize}
    \item Variables: all unknown cells in the 9-by-9 puzzle

	\item Domain: $\{1-9\}$

    \item Constraints
    \begin{itemize}
        \item No same value on a row
        \item No same value in a column
        \item The puzzle is divided into 9 cell groups, each of size 3-by-3. The
        third constraint is no same value in any of these groups.
    \end{itemize}
\end{itemize}

\section{Simulated Annealing Implementation}


\end{document}
